Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-22 theory.tex
added additional paper references

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97a,Rad97} encompass the familiar parton
distribution functions (PDFs) and nucleon form factors to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the H{\sc ermes}
collaboration has previously published results
\cite{Air06,Air08,Air09,Air10,Air10a} on
the leptoproduction of real photons from a \blue{nucleus} that can be used to
constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a
hard scattering kernel with a GPD that describes a soft part of the scattering
process.

>>>>

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97a,Rad97} encompass the familiar parton
distribution functions (PDFs) and nucleon form factors to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the H{\sc ermes}
collaboration has previously published results
\cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
the leptoproduction of real photons from a \blue{nucleus} that can be used to
constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a
hard scattering kernel with a GPD that describes a soft part of the scattering
process.
